%!TEX root = thesis.tex
As mentioned in our definition of AHIs in chapter~\ref{ch:adhoc} we proposed three different approaches to creating AHIs.
In this chapter we will explore the first approach that was to use shape-change as a construction mechanism for AHIs
So in this chapter we will dig in to the area of shape-changing interfaces to explore and illustrate the possibilities of creating AHIs based on shape-change.
More specifically we will touch upon a specific approach to constructing SCIs called jamming.

SCIs were introduced in the introduction of this thesis as interfaces that use physical change of shape as input or output.
Jamming is special kind of technique that can be used to control the stiffness of a material which makes it possible to construct objects that can change their surface structure.

What makes SCIs interesting to AHIs is it's ability to dynamically change the physical properties of an interface element, be it shape, texture, stiffness, position ect.
This change in physicality can then be the offset for a new temporary interaction possibility that is created for the specific situation, where afterwards it can return to it's initial natural state.
Compared to TUIs, SCIs have to ability to for a dynamic relationship between the physical objects and the digital state of the system, allowing both the user and the computer to change the physical state of an object to match its digital state.
These aspect aligns well with the definition of AHIs that we presented earlier in section~\ref{adhoc:definition}.
\blank
The process of our exploration of SCIs has, at times, been somewhat discouraging as we have proceeded to learned the lessons of the difficulty of creating such interfaces.
We have come to the conclusion that SCIs are indeed non-trivial to build and prototype, a lesson that we think everyone who has worked on SCIs must have experiences at some point, although it has not been widely mentioned in the literature. 

There are some inherently difficult aspects of creating objects with kinetic movements, for example in our earlier described BeoMotion project the change from flat surface to edged surface proved difficult as the phase change, because we worked with non-elastic materials, caused a contraction of the base structure.
We solved this by putting small rails on each of the individual elements of the structure to allow the contraction but this caused a new problem as small gaps now emerged since the base of the elements was able to move sightly in relation to each other.

In our exploration of jamming we also ran in to various problems.
While we consider ourselves fairly home in physical computing we, perhaps a little overconfident, initially thought it would be moderately straight forward to build pneumatic and hydraulic jamming systems.
We quickly ran into difficulties though with a seemingly continuous stream of new challenges in relation to vacuum pumps, compressors, solenoid valves, custom made membranes, various fittings and connectors between non-fitting tubes, particles and filters -- all elements that we had never worked with before.
On top of that all of these pieces had to work together while being air or water tight. 

So while we did not end up with a finished, ready-to-test prototype we did still, in our opinion, gain relevant experiences and additions to our notion of AHIs, in the shape of concrete experience with building AHIs, concept development and a study of the field of jamming and its relevance to AHIs. 

\section{A vocabulary of shape-change}
\label{ch:jamming:shape-change} 
\input{jamming/shape-change.tex}

\section{Jamming as an enabling technology}
\label{ch:jamming:enabling-technology} 
\input{jamming/technology.tex}

\section{Related work}
\label{ch:jamming:related-work} 
\input{jamming/related-work.tex}

\section{Concepts}
\label{ch:jamming:concepts} 
\input{jamming/concepts.tex}

\section{Discussion}
\todo{Maybe some Gaver (research through design) and (Alternatives, conceptual design proposals )}